%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {École Polytechnique, LIX} % Institution
    {Ph.D. in Character Animation and Computer Graphics} % Degree
    {Palaiseau, France} % Location
    {Oct. 2020 - Oct. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Topic: Efficient Models for Human Locomotion and Interaction in Natural Environments.}
        \item {Supervisors: \textbf{Prof. Damien Rohmer} and \textbf{Prof. Marie-Paule Cani}.}
        \item {Funding: European Union’s Horizon 2020 Research Programme. Marie Skłodowska-Curie Grant Agreement n. 860768 (CLIPE project).}
      \end{cvitems}
    }

  %---------------------------------------------------------
  \cventry
    {Albert-Ludwigs-Universität Freiburg} % Institution
    {M.Sc. in Embedded Systems and AI} % Degree
    {Freiburg, Germany} % Location
    {Apr. 2017 - Nov. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Framework: Robotics, Computer Vision, Machine Learning, Deep Learning and Reinforcement Learning.}
        \item {Thesis: Deep Multimodal Learning for Autonomous Driving.}
        \item {Supervisors: \textbf{Prof. Joschka Bödecker} and \textbf{Prof. Abhinav Valada}.}
      \end{cvitems}
    }

  %---------------------------------------------------------
  \cventry
    {Universidad Carlos III - Poznan University of Technology (ERASMUS)} % Institution
    {B.Sc. in Electronics and Automation Engineering} % Degree
    {Madrid, Spain} % Location
    {Sep. 2010 - Sep. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Framework: Digital/Analog Electronics, CS, Robotics and Control Engineering.}
        \item {Thesis: Development of a localization-based AR framework in C++ for smart glasses.}
        \item {Supervisors: \textbf{Prof. Angel Garcia Crespo}.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
